Ceph Parallel File System Evaluation Report

### 2013-08-28 ceph-initial.tex
changes here and there

\begin{itemize}
\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
perform a sync operation.  This is a more realistic use case scenario than just
open, close and removal sequence of metadata operations.

\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
clients, the total number of files and directories in the workload is 8,000. Since we did not specify
either \verb!-D! or \verb!-F!, this is a mixture of both.

@@

\item \verb!-u!: without this option, we are exercising shared directory; with
this option, we are exercising unique directories.

@@

\item While the other operations seems unaffected or flat by the number of
clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
contention for shared directory. The performance degradation amount to 50\% or
more.

>>>>

\begin{itemize}
\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
perform a sync operation.  This is a more realistic use case scenario than just
open, close and unlink sequence of metadata operations.

\item \verb!-n 1000!: Per client file \textit{and} directory workload. For
eight clients, the total number of files and directories in the workload is
8,000. Since we did not specify either \verb!-D! (indicates a directory only
workload) or \verb!-F! (indicates a file only workload), this is a mixture of
both directory and file workloads.

@@

\item \verb!-u!: without this option, we are exercising shared directory; with
this option, we are exercising unique directories per test client processes.

@@

\item While the other operations seems unaffected or performance remains the
same by the number of clients, it is not so if we zoom in, see
figures \ref{fig:mdtest-fcreate} and \ref{fig:mdtest-dcreate}:  as number of clients
increases, we observed the contention for shared directory. The performance
degradation amount to 50\% or more.

### 2013-08-28 ceph-tuning.tex
changes here and there

We ran a script written by Inktank for internal Ceph testing to perform
sweeps over Ceph configuration parameters to examine how different
tuning options affect performance on the DDN platform. The result of this
parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
to Appendix E for explanations of these probed parameters.

@@

During these tests, a trend that previously had been seen became more
apparent.  During reads, there were periods of high performance followed by
periods of low performance or outright stalls that could last for up to 20
seconds at a time.  After several hours of diagnostics, Inktank observed that
outstanding operations on the clients were not being shown as outstanding on
the OSDs.  This appeared to be very similar to a problem Jim Schutt at Sandia
National labs encountered with TCP autotuning in the Linux
kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically
adjusts the TCP receive window for each connection based on link conditions
such as bandwidth delay product. We have observed this will make a notable
improvement on Ceph read performance, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

Recent versions of Ceph work around this issue by manually controlling the TCP
buffer size.  The testing at ORNL directly influenced and motivated the creation
of this feature!

>>>>

We swept over Ceph configuration parameters to examine how different tuning
options affect performance on the DDN platform. The result of this parameter
probing is illustrated in Figure~\ref{fig:parametric}. Please refer to Appendix
E for explanations of these probed parameters.

@@

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time.
After running diagnostics, we observed that outstanding operations on the
clients were not being shown as outstanding on the OSDs.  This appeared to be
very similar to a problem Jim Schutt at Sandia National labs encountered with
TCP autotuning in the Linux
kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this improving the performance
significantly on Ceph read operations, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

Recent versions of Ceph work around this issue by manually controlling the TCP
buffer size.
